My title

### 2024-02-11 outputs/paper/paper.qmd
fixing commit

#reading cleaned data
rhode = read_csv(
  file = here("outputs/data/cleaned_learningmodel/rhode.csv"),       
  show_col_types = FALSE
)

@@

Talk more about it.

@@

@@

Our results are summarized in @tbl-modelresults.

>>>>

#reading cleaned data

state_score = read_csv(file = here("outputs/data/cleaned_state_scoredata.csv"),       
  show_col_types = FALSE
)

head(state_score)

rhode = read_csv(
  file = here("outputs/data/cleaned_learningmodel/rhode.csv"),       
  show_col_types = FALSE
)

@@

Talk more about it., SURE

@@

data_2019 <- state_score %>% 
  filter(year == 2019) %>%
  group_by(state) %>%
  summarise(
    avg_share_inperson = mean(share_inperson, na.rm = TRUE),
    avg_share_virtual = mean(share_virtual, na.rm = TRUE),
    avg_share_hybrid = mean(share_hybrid, na.rm = TRUE),
    avg_participation = mean(participation, na.rm = TRUE),
    avg_pass_rate = mean(pass, na.rm = TRUE)
  )

data_2021 <- state_score %>% 
  filter(year == 2021) %>%
  group_by(state) %>%
  summarise(
    avg_share_inperson = mean(share_inperson, na.rm = TRUE),
    avg_share_virtual = mean(share_virtual, na.rm = TRUE),
    avg_share_hybrid = mean(share_hybrid, na.rm = TRUE),
    avg_participation = mean(participation, na.rm = TRUE),
    avg_pass_rate = mean(pass, na.rm = TRUE)
  )

# Format the tables using kable and kableExtra
kable_2019 <- data_2019 %>%
  kable(format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "scale_down"))

# Print the kable formatted tables
print(kable_2019)

@@

Our results are summarized in @tbl-modelresults.
The table
